---
title: "My Reveal.js Demo"
subtitle: "Create beautiful interactive slide decks with Reveal.js"
format:
  revealjs: 
    slide-number: true
    chalkboard: 
      buttons: false
    preview-links: auto
    logo: images/quarto.png
    css: styles.css
    footer: '[https://{{< meta prerelease-subdomain >}}quarto.org](https://{{< meta prerelease-subdomain >}}quarto.org)'
#runtime: shiny
---

## Welcome {.emphasize}

**Quarto** enables you to weave together content and executable code into a finished presentation. To learn more about Quarto presentations see <https://quarto.org/docs/presentations/>.

---
<!-- ## What is Quarto? {.em}phasize} -->

<!-- **Quarto** is an open-source scientific and technical publishing system built on Pandoc. It enables you to create dynamic documents, reports, presentations, and websites in R, Python, Julia, and Observable JavaScript. -->

<!-- **Quarto** is a next-generation version of R Markdown, and it is designed to be a unified authoring system for all your technical writing. -->

<!-- --- -->

## Today {.emphasize}

This is a Quarto Reveal.js presentation. It is a demo of the Reveal.js format and some of its features, including:

- Custom theme
- Data visualizations using **ggplot2** and **plotly**
- Interactive slides
---

## Data Visualization {.emphasize}

```{r}
library(ggplot2)
ggplot(mtcars, aes(x = mpg, y = wt)) +
  geom_point(color = "steelblue", size = 3) +
  labs(title = "Fuel Efficiency vs. Weight",
       x = "Miles per Gallon (mpg)",
       y = "Weight (1000 lbs)") 
```

---
## Interactivity with $plotly$ {.emphasize}

```{r}
library(plotly)

p <- ggplot(mtcars, aes(x = mpg, y = wt)) +
  geom_point(color = "steelblue", size = 3) +
  labs(title = "Fuel Efficiency vs. Weight",
       x = "Miles per Gallon (mpg)",
       y = "Weight (1000 lbs)")

ggplotly(p, width = 900, height = 400)
```
---
## Live Poll: What's Your Favorite Visual Design Principle?

<iframe src="https://app.sli.do/event/gPHvXsfj7Sexn3HGAKi4cW" 
height="100%" width="100%" frameBorder="0" style="min-height: 560px;
" allow="clipboard-write" title="Slido"></iframe>

_Note: Use <kbd>Esc</kbd> to exit full screen._

```






